% Cullen Taylor -- Resume
% Contents Copyright (C) 2017 - 2018, Cullen Taylor

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[12pt]{article} % Set default font size to 12pt
\input{preamble}
\begin{document}

\centerline{{\Huge \bf Cullen Taylor}}
\bigskip

\contact{cullen@eggshell.me}
        {gitlab.com/eggshell}
        {Brooklyn, NY}
        {}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Technical}
      {Infrastructure, Containers, Kubernetes, Config Management}

\skill{Development}
      {shell, python, node.js, golang}

\skill{Soft Skills}
      {Technical Marketing, Public Speaking, Advocacy}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
%\squish
\experience{GitLab}
           {Technical Marketing Manager - Cloud Native}
           {03/2019 - 01/2020}

Created and lead Knative workshops given at major open source conferences.

Created and gave technical demos for analyst briefings, conference booths and
internal enablement demonstrating ability of the product to create and interact
with Kubernetes resources, as well as run serverless workloads.

Worked heavily with partner vendors such as VMware and Google to create stage
content and whitepapers demonstrating various features of the product as they
related to the Cloud Native ecosystem.

\experience{IBM Open Technology}
           {Developer Advocate}
           {01/2017 - Present}

Assisted in creating and leading Kubernetes workshops for attendees at open
source conferences all over the world.

Assisted in forming a video streaming initiative to allow our developer
advocates to talk directly to a captive audience via Twitch and YouTube.

Assisted in forming partnerships with external clients in both the Cloud Native
technology space and gaming industry.

Developed an open source project which applied Object Character Recognition
and Machine Learning on Kubernetes to video game streams on Twitch.

\experience{IBM Cloud Infrastructure Services}
           {DevOps Engineer}
           {05/2015 - 01/2017}

Deployed and operated testing infrastructure for BlueBox integration to
facilitate post-acquisition releases.

Developed infrastructure tools and managed infrastructure for OpenStack-based
public clouds.

Overhauled documentation, continuous integration and containerization for
internal networking security project.
\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Texas State University}
           {}
           {2011-2015}

Bachelors Degree in Computer Science and Mathematics.
\end{description}

\heading{Speaking Engagements}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{DevOps Live @ TechWeek Frankfurt}
           {}
           {11/2019}

    ``Driving Innovation at an All-Remote Company''

\experience{KubeCon 2019, Velocity 2019, OSCON 2019}
           {}
           {05/2019 - 07/2019}

    ``Knative + GitLab Workshop''

\experience{OSCON 2018, Node Summit 2018}
           {}
           {07/2018}

    ``Applying Object Character Recognition and Kubernetes to Twitch''

\end{description}
\end{document}
